---
title: "Quickstart"
author: "Martin Barner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Generating fake data

**load package**

```{r}
library(xlsformfill)
```

**load questionnaire** choices and questions from csv as data frames

```{r}
questions <- read.csv("../tests/testthat/kobo questions.csv", stringsAsFactors = F)
choices <- read.csv("../tests/testthat/kobo choices.csv", stringsAsFactors = F)
```

**generate fake dataset** with ` n ` rows

```{r,message=FALSE,warning=FALSE}
fake_data <- xlsform_fill(questions,
                          choices,
                          n = 10)


```

```{r,results='asis',echo = F}
# knitr::kable(fake_data,format = 'markdown')

```

Take note of any warnings. Not all skiplogic and not all calculations will be calculated correctly if the questionnaire has issues. Advanced skiplogic functions may not be supported.

<!-- **Example Output** -->

<!-- ```{r,results='asis',echo=FALSE} -->
<!-- knitr::kable(fake_data) -->
<!-- ``` -->

**save to file**
```{r,eval=F}
write.csv(fake_data,"my_fake_data_file.csv")
```


### Supported Features

- respects ODK "`relevant`" skip logic (Some advanced functionality such as "coalesce()" not covered)
- ODK `calculation` variables translated to R and respective columns included
- adds UUID column
- adds both logical choice columns and concatenated column for select_multiple questions

**Supported ODK question types**

- integer
- decimal
- select_one
- select_multiple
- text
- deviceid
- start
- end
- dateTime

**ODK question types that are _not_ supported for now**

- geopoint
- geotrace
- geoshape
- audio
- video
- file
- barcode
- acknowledge
- hidden
- xml-external
- image
- range
- rank

